Designing Turk Experiments for Visual Statistical Inference

### 2013-06-12 paper_turk.tex
paper layout

Figure \ref{fig:amazon_task} shows how simple an MTurk task could be. It is possible to get a lineup evaluated by creating such a simple task. We just need to replace the picture in Figure \ref{fig:amazon_task} with the lineup in Figure \ref{fig:lineup_turk} and change the answering options. But some times we may need more than one lineups to be evaluated by an observer. There could be many lineups from which a small number lineups needs to be shown to an observer. All these could be done by creating a web application. For additional control we plan to separate this application from MTurk system. The following section discuss this in details.

@@

@@

\section{Web Application for Turk Experiment} We developed a web site to run the Amazon Mechanical Turk experiments.  PHP scripting language is used and embedded with HTML for designing the web site. Javascript is used for validating the input data and producing warning message.  We use  Amazon Mechanical Turk web site to recruit the participants and direct them to our web site to actually participate in the survey. This has allowed us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site to transfer data to our server.

@@

\section{Managing Turk Task} Turk workers are usually small payee workers. There several issues related to the payment of their effort. These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.

@@

\section{Turk Data Quality}

>>>>

Figure \ref{fig:amazon_task} shows how simple an MTurk task could be. It is possible to get a lineup evaluated by creating such a simple task. We just need to replace the picture in Figure \ref{fig:amazon_task} with the lineup in Figure \ref{fig:lineup_turk} and change the answering options. But some times we may need more than one lineups to be evaluated by an observer. There could be many lineups from which a small number lineups needs to be shown to an observer. It is convenient if the lineup is clickable so that selection of plot can be made by mouse click. All these could be done by creating a web application. For additional control we plan to separate this application from MTurk system. The following section discuss this in details.

@@

This paper is organized as follows. Section \ref{sec:turk_exp} presents the details description of an experiment and things to consider before a turk experiment. Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not possible through MTurk. Section \ref{sec:turk_task} describes how to create a MTurk task, mange workers and process payments. Finally Section \ref{sec:turk_data} presents some data obtained from various experiments done through the proposed web application and discusses about the quality of the data.

@@

\section{Web Application for Turk Experiment} \label{sec:web_application}

We developed a web site to run the Amazon Mechanical Turk experiments.  PHP scripting language is used and embedded with HTML for designing the web site. Javascript is used for validating the input data and producing warning message.  We use  Amazon Mechanical Turk web site to recruit the participants and direct them to our web site to actually participate in the survey. This has allowed us to get the data directly in a secure way from the web and we don't have to depend on the Mechanical Turk web site to transfer data to our server.

@@

\section{Managing Turk Task}\label{sec:turk_task}

Turk workers are usually small payee workers. There several issues related to the payment of their effort. These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.

@@

\section{Turk Data Quality} \label{sec:turk_data}
